Analyzing the Effects of the NBA COVID Bubble on the NBA Playoffs

### 2020-11-03 Manuscript/NBABubbleAnalysis.Rmd
Update NBABubbleAnalysis.Rmd

Unfortunately, this study is limited by a one time sample. It is unknown if there
will ever be another NBA playoffs played in this fashion. It seems unlikely that 
these conditions will ever be repeated. That being said, it does not seem like a 
follow-up study using the same measures with a different sample will ever be
possible. If possible, that type of study could help strengthen the conclusions
made in this paper.

>>>>

Unfortunately, this study is limited by a one time sample. It seems unlikely that 
these conditions will ever be repeated. That being said, it will not be possible
to have a follow-up study using the same measures with a different sample. If
possible, that type of study could help strengthen the conclusions
made in this paper.
